\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-10-23 doc/USER_MANUAL/manual_SPECFEM3D.tex
added a DG reference and a comment about discontinuous meshes to the manual

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,KoWoHu02,ChCaVi03,Kop06}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,BeLaPi06,DuKa06,DeSeWh08,WiStBuGh10,DeSe10}, with optimized efficiency because of its tensorized basis functions.
Effects due to lateral variations in compressional-wave speed, shear-wave
speed, density, a 3D crustal model, topography and bathymetry are
included. For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08} and
in particular \citet{KoLiTrSuStSh04}. If you use the 3D southern
California model, please cite \citet{SuSh03} (LA), \citet{lovelyetal06}
(Salton Trough), and \citet{hauksson2000} (southern California).
The Moho map was determined by \citet{zhu&kanamori2000}. The 1D SoCal
model was developed by \citet{DrHe90}. The package can accommodate
full 21-parameter anisotropy (see~\citet{ChTr07}) as well as lateral
variations in attenuation. Adjoint capabilities and finite-frequency
kernel simulations are included \citep{LiTr06,TrKoLi08}.

>>>>

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,KoWoHu02,ChCaVi03,Kop06}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,BeLaPi06,DuKa06,DeSeWh08,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions.
Note that in many (most?) geological models in the context of seismic wave propagation studies
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient.
Effects due to lateral variations in compressional-wave speed, shear-wave
speed, density, a 3D crustal model, topography and bathymetry are
included. For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08} and
in particular \citet{KoLiTrSuStSh04}. If you use the 3D southern
California model, please cite \citet{SuSh03} (LA), \citet{lovelyetal06}
(Salton Trough), and \citet{hauksson2000} (southern California).
The Moho map was determined by \citet{zhu&kanamori2000}. The 1D SoCal
model was developed by \citet{DrHe90}. The package can accommodate
full 21-parameter anisotropy (see~\citet{ChTr07}) as well as lateral
variations in attenuation. Adjoint capabilities and finite-frequency
kernel simulations are included \citep{LiTr06,TrKoLi08}.
